Generative adversarial neural networks model of photonic crystal fiber based Surface Plasmon Resonance Sensor

### 2020-10-20 docs/paper/paper.tex
Reply fixes by HA

The ANN model employed in this work is a fully connected feed-forward MLP network consisting of an input layer, an output layer, and 5 hidden layers. The ANN is designed and trained to estimate the confinement loss in a regression configuration. We have applied  $log_{10}$ to confinement loss calculation in order to keep its numeric stability across a wide range \cite{paper0}. Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function. Table  \ref{tbl:anndetails} summarizes the details of this model. \hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to a minimum.}

@@

We have performed experiments comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}. Results of this experiment are demonstrated in Figure \ref{chart:perfnoaug}. In the SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower. Therefore, they both have higher error rates compared to the PCF dataset. According to Figure \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ case, the ANN method proposed in \cite{paper0} does not fit to the curve caused by the change in the wavelength. 
%This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
Regardless of this, both models have similar MSE due to the shift in the curve fit. Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.

@@

		\end{axis}
		\end{tikzpicture}
		\caption{\dszero{} dataset}
	\end{subfigure}
	\vspace{0.75cm}

	\begin{subfigure}{\textwidth}
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ({$n_{analyte=1.34}$}), 
		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		height=6cm,
		legend pos=north west
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		]
		table[x={wave},y={predicted}]{data/wave_134_their.txt};
		\addlegendentry{\cite{paper0}}

		\addplot[
		only marks,
		mark size=2.9pt, mark=x, color=green!50!black
		]
		table[x={wave},y={predicted}]{data/wave_134_our.txt};
		\addlegendentry{$Proposed$}

@@

		\legend{}
				legend style={anchor=north east,draw=none,fill=none,font=\tiny, at={(axis cs:670,1.55)}},

@@

		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE: 0.08721}
		\addlegendimage{second}\addlegendentry{Proposed MSE: 0.18869 }

		\end{axis}
		\end{tikzpicture}
		%
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $ ($n_{analyte=1.35}$), 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		height=6cm,
		legend pos=north west
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table[x={wave},y={predicted}]{data/wave_135_their.txt};
		\addlegendentry{\cite{paper0}}

@@

		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE:0.17491}
		\addlegendimage{second}\addlegendentry{Proposed MSE:0.37049 }

		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset.
		\\\hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 \mu m$ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m$ $ d_3 = 0.35 \mu m $.}\\ \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m  $.}		
		  }
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		\end{axis}
		\end{tikzpicture}
		\caption{\dszero{} dataset}
	\end{subfigure}
	\vspace{0.75cm}

	\begin{subfigure}{\textwidth}
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.34}$},
		width=0.48\textwidth,
		legend pos=north east,
		height=6cm
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		]
		table[x={wave},y={predicted}]{data/wave_134_our.txt};
		\addlegendentry{Without GAN}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.18869}
		\addlegendimage{second}\addlegendentry{With GAN:0.11670 }

		\end{axis}
		\end{tikzpicture}
		%
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		title={$n_{analyte=1.33}$},
		width=0.48\textwidth,
		legend pos=north east,
		height=6cm
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table[x={wave},y={predicted}]{data/wave_133_our.txt};
		\addlegendentry{Without GAN}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.32373}
		\addlegendimage{second}\addlegendentry{With GAN:0.08664 }
		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset. 
		\\ \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 \mu m $ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m $.} \\ \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.55 \mu m $ $ d_3 = 0.15 \mu m $.} 
		}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}

>>>>

The ANN model employed in this work is a fully connected feed-forward MLP network consisting of an input layer, an output layer, and 5 hidden layers. The ANN is designed and trained to estimate the confinement loss in a regression configuration. We have applied  $log_{10}$ to confinement loss calculation in order to keep its numeric stability across a wide range \cite{paper0}. Each hidden layer contains 50 neurons and uses Rectified Linear Unit (ReLU) activation function. Table  \ref{tbl:anndetails} summarizes the details of this model. \hl{The number of hidden layers and neurons are empirically determined to be able to estimate the loss curve while keeping the complexity of the network to a minimum. With these changes, the proposed network is able to predict more complex functions, however, it will also require more training samples.}

@@

We have performed experiments comparing the proposed ANN architecture with the state-of-the-art method proposed in \cite{paper0}. Results of this experiment are demonstrated in Figure \ref{chart:perfnoaug}. In the SPR dataset experiment, ANN models are predicting a new configuration and the number of samples available for training is lower. Therefore, they both have higher error rates compared to the PCF dataset. \hl{According to Figure} \ref{chart:perfnoaug}c, $n_{analyte} = 1.35$ \hl{case, the ANN method proposed in }\cite{paper0}\hl{ is not a good predictor of the shape of the curve caused by the change in the wavelength, even though it fits this curve much better than the proposed method, showing that the proposed method requires more samples for training.}
%This can be linked to the fact that this method uses full-batch learning and therefore under-fits the model \cite{keskar2016large}.
Regardless of this, both models have similar MSE due to the shift in the curve fit. Since the network is never exposed to this particular geometric configuration shift in the curve fit occurs.

@@

		\end{axis}
		\end{tikzpicture}
		\caption{\dszero{} dataset}
	\end{subfigure}
	\vspace{0.5cm}

	\begin{subfigure}{\textwidth}
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$ Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		height=6cm,
		legend pos=north east,
		legend style={font=\footnotesize}
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		]
		table[x={wave},y={predicted}]{data/wave_134_their.txt};

		\addplot[
		only marks,
		mark size=2.9pt, mark=x, color=green!50!black
		]
		table[x={wave},y={predicted}]{data/wave_134_our.txt};

@@

		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE: 0.09}
		\addlegendimage{second}\addlegendentry{Proposed MSE: 0.19 }

@@

		\end{axis}
		\end{tikzpicture}
		%
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		height=6cm,
		legend pos=north west,
		legend style={font=\footnotesize}
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table[x={wave},y={predicted}]{data/wave_135_their.txt};
		\addlegendentry{\cite{paper0}}

@@

		\addlegendimage{first}\addlegendentry{\cite{paper0} MSE:0.17}
		\addlegendimage{second}\addlegendentry{Proposed MSE:0.37 }

		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset. \hl{Left: $ n_{analyte} = 1.34 $ $ n_{eff} = 1.46$ $ \Lambda = 0.24 \mu m$ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m$ $ d_3 = 0.35 \mu m $.} \hl{Right: $ n_{analyte} = 1.35 $	$ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m  $.}		
		  }
	\end{subfigure}
	\caption{Testing results without GAN augmentation phase}
	\label{chart:perfnoaug}
\end{figure*}

@@

		\end{axis}
		\end{tikzpicture}
		\caption{\dszero{} dataset}
	\end{subfigure}
	\vspace{0.5cm}

	\begin{subfigure}{\textwidth}
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$Loss $ $ in $ $ Log(db/cm) $,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		legend pos=north east,
		height=6cm,
		legend style={font=\footnotesize}
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		]
		table[x={wave},y={predicted}]{data/wave_134_our.txt};
		\addlegendentry{Without GAN}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.19}
		\addlegendimage{second}\addlegendentry{With GAN:0.12 }

		\end{axis}
		\end{tikzpicture}
		%
		\begin{tikzpicture}
		\begin{axis}[
		xlabel=$Wavelength(\lambda) $  $ in $  $ nm $, 
		ylabel=$~$,
		grid=both,
		minor grid style={gray!25},
		major grid style={gray!25},
		width=0.48\textwidth,
		legend pos=north east,
		height=6cm,
		legend style={font=\footnotesize}
		]
		\addplot[
		only marks,
		mark size=2.9pt, mark=o, color=red, fill=red
		] 
		table[x={wave},y={predicted}]{data/wave_133_our.txt};
		\addlegendentry{Without GAN}

@@

		\addlegendimage{first}\addlegendentry{Without GAN:0.32}
		\addlegendimage{second}\addlegendentry{With GAN:0.09 }
		\end{axis}
		\end{tikzpicture}
		\captionsetup{justification=centering}
		\caption{Configuration estimation on SPR dataset. \hl{Left: $n_{analyte} = 1.34$ $ n_{eff} = 1.46 $ $ \Lambda = 0.24 \mu m $ $ d_1 = 0.45 \mu m $ $ d_2= 0.75 \mu m $ $ d_3 = 0.35 \mu m $.} \hl{Right: $n_{analyte} = 1.33 $ $ n_{eff} = 1.45 $ $ \Lambda = 0.15 \mu m $ $ d_1 = 0.25 \mu m $ $ d_2= 0.55 \mu m $ $ d_3 = 0.15 \mu m $.} 
		}
	\end{subfigure}
	\caption{GAN Phase experimental results}
	\label{chart:ganperf}
\end{figure*}
